---
title: "Reduce Items - Calculate Alpha"
author: "Petra Isenberg"
date: "3/24/2022"
output: html_document
---


This code calculates the average ratings each image received from participants and saves them as plots with CIs. 
This analysis is partly exploratory as we check what would have happened if participants had used some of our reduced scale.

# Setup

```{r}
source("CI-Functions.R")
participantResponseFiles <- list.files(path= "./data",pattern = "\\.csv$") #names correspond to images, one participant per row, one word per
```

# Functions
This one cleans up the column names for each image's responses
```{r}
cleanColnames <- function(data){
  newNames <- gsub("^.+?\\.(.+?)\\..*$", "\\1", colnames(data))
  return(newNames)
}
```

This functions draws a bar chart with confidence intervals
```{r}
barChart <- function(resultTable, techniques, nbTechs = -1, ymin, ymax, xAxisLabel = "I am the X axis", yAxisLabel = "I am the Y Label",plotTitle){
  #tr <- t(resultTable)
  if(nbTechs <= 0){
    stop('Please give a positive number of Techniques, nbTechs');
  }
  
  tr <- as.data.frame(resultTable)
  nbTechs <- nbTechs - 1 ; # seq will generate nb+1
  
  #now need to calculate one number for the width of the interval
  tr$CI2 <- tr$upperBound_CI - tr$mean
  tr$CI1 <- tr$mean - tr$lowerBound_CI
  
  #add a technique column
  tr$technique <- factor(seq.int(0, nbTechs, 1));
  
  breaks <- c(as.character(tr$technique));
  print(tr)
  g <- ggplot(tr, aes(x=technique, y=mean)) + 
    #   geom_bar(stat="identity",fill = I("#CCCCCC")) +
    geom_errorbar(aes(ymin=mean-CI1, ymax=mean+CI2),
                  width=0,                    # Width of the error bars
                  size = 1.1
    ) +
    #labs(title="Overall time per technique") +
    labs(x = xAxisLabel, y = yAxisLabel) + 
    scale_y_continuous(limits = c(ymin,ymax),breaks=1:7) +
    scale_x_discrete(name="",breaks,techniques)+
    coord_flip() +
    ggtitle(plotTitle) +
    theme(panel.background = element_rect(fill = 'white', colour = 'white'),axis.title=element_text(size = rel(1.2), colour = "black"),axis.text=element_text(size = rel(1.2), colour = "black"),panel.grid.major = element_line(colour = "#DDDDDD"),panel.grid.major.y = element_blank(), panel.grid.minor.y = element_blank())+
    geom_point(size=2, colour="black")         # dots
  
  print(g)
}
```

This next function calculates the CIs of each image's responses depending on the scale items (terms) given. 
```{r}
calculateDrawResponseCIs <- function(scaleItems){


  imageCount <- length(participantResponseFiles)
  pointEstimateVector = c()
  lowerBoundVector = c()
  upperBoundVector = c()
  imageVector = c()
  
  for (image in 1:imageCount){
  
    data <- read.csv(paste("data/",participantResponseFiles[[image]],sep=""), encoding="UTF-8")
    #terms <- cleanColnames(data) 
    #colnames(data) <- terms
    
    #exploratory trying to see what would happen if we had had a lot fewer participants
    #data <- data[sample(nrow(data), 24), ]
    
    data <- data[scaleItems]
  
    means <- rowMeans(data)
    
    imageVector <- append(imageVector,image)
    ci <- bootstrapMeanCI(means)
    pointEstimateVector <- append(pointEstimateVector,ci[1])
    upperBoundVector <- append(upperBoundVector,ci[3])
    lowerBoundVector <- append(lowerBoundVector,ci[2])
  }
  
  df <- data.frame(image=imageVector,mean=pointEstimateVector,lowerBound_CI=lowerBoundVector,upperBound_CI=upperBoundVector)
  plotTitle <- paste(paste("Average Rating for the",length(scaleItems)),"item scale")
  barChart(df,df$image ,nbTechs = imageCount, ymin = 1, ymax = 7, "Image", "Average Ratings",plotTitle)
  ggsave(paste("./generatedPlots-CFA/",paste(plotTitle,".pdf",sep=""),sep=""), width=8, height=4)
  
  print(df)
  
  return(df)
}
```

As the ratings per image were done by different participant pools we don't actually want to compare the ratings of each image.
```{r}
generatePerImageTables <-function(dfs,titles){
  imageCounts <- length(participantResponseFiles)

  for(i in 1:imageCounts){
    pointEstimateVector = c()
    lowerBoundVector = c()
    upperBoundVector = c()
    scaleVector = c()
    
    dflength <- length(dfs)
    for(d in 1:dflength){
      scaleVector <- append(scaleVector,titles[d])
      df <- dfs[[d]]
      
      pointEstimateVector <- append(pointEstimateVector,df$mean[df$image==i])
      upperBoundVector <- append(upperBoundVector,df$upperBound_CI[df$image==i])
      lowerBoundVector <- append(lowerBoundVector,df$lowerBound_CI[df$image==i])
    }
    
    df <- data.frame(scale=scaleVector,mean=pointEstimateVector,lowerBound_CI=lowerBoundVector,upperBound_CI=upperBoundVector)
    plotTitle <- paste(paste("Image",i)," Ratings Per Scale")
    barChart(df,df$scale ,nbTechs = dflength, ymin = 1, ymax = 7, "Image", "Average Ratings",plotTitle)
    path<-paste("./generatedPlots-CFA/",paste(plotTitle,".pdf",sep=""),sep="")
    print(path)
    ggsave(path, width=8, height=4)
  }
}
```

And now we run our tests

## Average Ratings for the Test Scale

```{r}
data <- read.csv(paste("data/",participantResponseFiles[[1]],sep=""), encoding="UTF-8")
scaleItems <- colnames(data)
df31 <- calculateDrawResponseCIs(scaleItems)
```



